CS6213 Project Report

### 2021-05-07 report/paper.tex
Empirical

>>>>

\paragraph{Empirical evidence.}
%
We have some evidence that this strategy is effective at exploring states that would otherwise not be reached by TLC within any reasonable amount of time.
%
Daniel Ricketts' specification (partly proven in TLAPS) has two properties that are in fact \emph{incorrect}, \ie they are not satisfied by Raft.
%
These properties, which we renamed \texttt{VotesGrantedInv\_false} and \texttt{LeaderCompleteness\_false} in our spec, are violated by traces that extend our ``two leaders at the same time'' scenario.
%
Since these properties were included in Ricketts' spec, which we assume he model checked, we conclude that he did not model-check his specification to the required diameter (trace length) of around 27.
%
In our estimation, even with heavy constraints, it would take several days to reach that diameter with TLC's normal mode of operation.
